\textbf{SPECFEM3D Cartesian}\\ \textbf{User Manual}

### 2017-04-10 doc/USER_MANUAL/02_getting_started.tex
better sentence for Intel ifort

Before running the \texttt{configure} script, you should probably
edit file \texttt{flags.guess} to make sure that it contains the best
compiler options for your system. Known issues or things to check
are:
\begin{description}
\item [{\texttt{Intel ifort compiler}}] See if you need to add \texttt{-assume byterecl} for your machine. \textbf{In the case of that compiler, we have noticed that versions dot zero sometimes have bugs or issues that can lead to wrong results when running the code, thus we \emph{strongly} recommend using versions dot one or above (for instance version 13.1 instead of 13.0, version 14.1 instead of 14.0 and so on)}.
\item [{\texttt{IBM compiler}}] See if you need to add \texttt{-qsave}
or \texttt{-qnosave} for your machine.
\item [{\texttt{Mac OS}}] You will probably need to install \texttt{XCODE}.
\end{description}
When compiling on an IBM machine with the \texttt{xlf} and \texttt{xlc}
compilers, we suggest running the \texttt{configure} script with the
following options:

>>>>

Before running the \texttt{configure} script, you should probably
edit file \texttt{flags.guess} to make sure that it contains the best
compiler options for your system. Known issues or things to check
are:
\begin{description}
\item [{\texttt{Intel ifort compiler}}] See if you need to add \texttt{-assume byterecl} for your machine. \textbf{In the case of that compiler, we have noticed that initial release versions sometimes have bugs or issues that can lead to wrong results when running the code, thus we \emph{strongly} recommend using a version for which at least one service pack or update has been installed.}
\item [{\texttt{IBM compiler}}] See if you need to add \texttt{-qsave}
or \texttt{-qnosave} for your machine.
\item [{\texttt{Mac OS}}] You will probably need to install \texttt{XCODE}.
\end{description}
When compiling on an IBM machine with the \texttt{xlf} and \texttt{xlc}
compilers, we suggest running the \texttt{configure} script with the
following options:
